---
title: "Lab 08 - University of Edinburgh Art Collection"
author: "Benjamin Egan"
date: "03/03/25"
output: github_document
---

## Load Packages and Data  

First, let's load the necessary packages:  

```{r load-packages, message = FALSE, echo = FALSE}
library(tidyverse) 
library(skimr)
library(robotstxt) #use to see if can use paths_allowed
library(rvest)
library(magrittr)
library(skimr)

paths_allowed("https://collections.ed.ac.uk/art)")

```

Now, load the dataset. If your data isn't ready yet, you can leave `eval = FALSE` for now and update it when needed.  


```{r load-data, message = FALSE, echo = FALSE}
uoe_art <- read_csv("data/uoe-art.csv")
view(uoe_art)
```

## Exercise 9

Let's start working with the **title** column by separating the title and the date:  

```{r separate-title-date, error = TRUE}
uoe_art <- uoe_art %>%
  separate(title, into = c("title", "date"), sep = "\\(") %>%
  mutate(year = str_remove(date, "\\)") %>% as.numeric()) %>%
  select(title, artist, year, link)
```

The code was already provided, so I didn't change anything. I'm guessing the error related to "expected two pieces" is because not all pieces had both a year and an author. I can see no author in some rows (182, 533, etc.) but not in all of them. I'm also guessing that they filled in these missing pieces with "NA." There were probably rows that didn't have parentheses around years, adding to the confusion. One of the rows just gave us a "2" for the year, probably adding to the confusion about including the year.


```{r skim}
skim(uoe_art)

uoe_art %>%
  ggplot(aes(
    x = year
  ))+
  geom_bar()
summary(uoe_art)
```


Using skim(), it appears that there are 111 artists missing from the data frame. It also appears there are 1580 data missing from the year column. One of the paintings shows a painting to be from the year 2. Death mask had an additional number in the sequence. The year should be 1964.

```{r filter}

uoe_art_mutated <- uoe_art %>%
  mutate(year1 = case_when(
    year == "2" ~ "1964"
  ))


uoe_art_filtered %>%
  ggplot(aes(
    x = year
  ))+
  geom_bar()
view(uoe_art_mutated)
```

## Exercise 10  

*Write your answer here.*  

Feel free to add code chunks as needed. Don't forget to label your code chunk.


## Exercise 11  


*Continue with the same structure as above.*

You're doing great—keep going! Follow the same format and add your response below.  


## Additional Exercises  

Almost there! Keep building on your work and follow the same structure for any remaining exercises. Each exercise builds on the last, so take your time and make sure your code is working as expected.  
